Named Entity Recognition as Structured Prediction

### 2012-11-11 doc/report/paper.tex
+conc.

In this paper, we presented a \namedentity~Recognition system based on the concept of Structured Prediction. While the system does not achieve state-of-the-art performance on the CoNLL shared task, we believe that the results are res

>>>>

In this paper, we presented a \namedentity~Recognition system based on the concept of Structured Prediction. While the system does not achieve state-of-the-art performance on the CoNLL shared task, we believe that the results are reasonable for the following reasons. We are using a simple model, which has the advantage that the final application will be fast and it is easily extendable. In contrast to the best systems in the CoNLL task, we also do not use ensemble learning methods and we use the same set of features for all languages, which enables simple extension of the system to additional languages.
